---
title: "Marketing Analytics"
author: "Hovik Voskanyan"
date: "2024-10-17"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r cars}
library('ggplot2')
library('ggpubr')
library('knitr')
library(readxl)
library(diffusion)
```

I chose to analyze stroller Innovation that gives a benefit to carry a luggage a long with children (https://time.com/collection/best-inventions-2022/6224793/ternx-carry-on/) and then I've found historical sales data in North Americas stroller market that as the product itself is designed by North American market it is sensible to analyze their market first.

The link to data is attached in readme file 

Scope : I have to analyze US's Stroller Market 


```{r}
#read Data

data<- read_excel("../data/StrollerSalesData.xlsx")

data$Sales = data$Sales * 1000000

head(data)
```

```{r}

sm_sales = ggplot(data = data, aes(x = Year, y = Sales)) +
geom_bar(stat = 'identity') +
ggtitle('Smartphone sales, mln units')

ggarrange(sm_sales)
```




Now we define model
```{r}
sales = data$Sales
t = 1:length(sales)
bass_m = nls(sales ~ m*(((p+q)^2/p)*exp(-(p+q)*t))/(1+(q/p)*exp(-(p+q)*t))^2,start=c(list(m=sum(sales),p=0.02,q=0.4)))

summary(bass_m)
# I kin

```
Now we see the estimated parameters
we need bass Model functions
```{r}
bass.F <- function(t, p, q) {
  numerator <- 1 - exp(-(p + q) * t)
  denominator <- 1 + (q / p) * exp(-(p + q) * t)
  return(numerator / denominator)
}

bass.f <- function(t, p, q) {
  F_t <- bass.F(t, p, q)
  return(p + q * F_t)
}
```


```{r}
time_ad = ggplot(data.frame(t = c(1:14)), aes(t)) +
stat_function(fun = bass.f, args = c(p=4.503e-02, q=9.761e-02)) +
labs(title = 'f(t)')

ggarrange(time_ad, sm_sales)

```
Calculating estimations using diffusion
```{r}
diff_m = diffusion(sales)
p=round(diff_m$w,4)[1]
q=round(diff_m$w,4)[2]
m=round(diff_m$w,4)[3]
diff_m
```

SCOPE : Our Scope is bounded in North Amerika's market as we are analyzing Sales in North America only

```{r}
data.frame(Predicted=log(q/p)/(p+q),
Actual=which.max(data$Sales))
```


